Effectiveness of community-based TURF-reserves in small-scale fisheries

### 2018-12-05 docs/Villasenor-Derbez.Rmd
Added caveats to socioeconomic data to close #30

>>>>

Our analyses of socioeconomic indicators has two limitations. First, we only look at landings and revenues by landings for communities with and without TURF-reserves. There are a number of other possible indicators that could show a change due to the implementation of the reserve. Notably, one often cited in the literature is additional benefits, such as tourism \citep{viana_2017}. However, it is unlikely that the evaluated communities will experience tourism benefits due to their remoteness and the lack of proper infrastructure to sustain tourism.

A second limitation of our socioeconomic analysis is that we do not observe effort data, which may mask the effect of the reserve. For example, if catches remain relatively unchanged but fishing effort decreased, that would imply a larger catch per unit effort. Even without changes to revenues, a lower input of effort (*e.g.* less fishing hours, less trips, less fuel) would imply that the fishery is more profitable. However, fishers are assambled into fishing cooperatives, meaning that profits are shared amongst all members \citep{mccay_2014,mccay_2017}. Therefore, the same revenue is still shared by the same amount of fishers.
